The \dealii Library, Version 9.1

### 2019-05-10 9.1/paper.tex
Address a few of the open issues.

The major changes of this release are:
\begin{itemize}
\item Improved support for automatic and symbolic differentiation;
\item Support for $hp$ adaptivity on MPI-parallel programs with \texttt{parallel::distributed::Triangulation}
\item Four new tutorial programs step-61, step-62, step-63, step-64.
\end{itemize}
These will all be discussed in more detail in the
following section. In addition, this release contains the following changes:
\begin{itemize}
\item ParsedConvergenceTable
\item FE\_BernardiRaugel
\item ConstraintMatrix class has been renamed to AffineConstraints
\item FE\_NedelecSZ
\item A number of bug fixes and performance improvements to the matrix-free framework and related geometric multigrid solvers were added. In particular, the implementation of the Chebyshev iteration, an often used smoother in the matrix-free context, has been revised to reduce the vector access. The performance improvement speed up matrix-free multigrid solvers by up to 10-15\% on affine geometries and up to 5\% on curved geometries.
\end{itemize}
Beyond these changes, the changelog lists more than 200 other features and bugfixes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tutorial and code gallery programs}

@@

The 9.1 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_8_5_0_and_9_0_0.html}
     {around 15 incompatible changes}; see \cite{changes91}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions, and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item TODO
\end{itemize}

@@

Older releases of \dealii can be cited as
\cite{dealII80,dealII81,dealII82,dealII83,dealII84,dealII85,dealII90}.

>>>>

The major changes of this release are:
\begin{itemize}
\item Improved support for automatic and symbolic differentiation;
\item Full support for $hp$ adaptivity in parallel computations;
\item Four new tutorial programs step-61, step-62, step-63, step-64,
  as well as one new code gallery program.
\end{itemize}
These will all be discussed in more detail in the
following section. There are a number of other noteworthy changes in this release:
\begin{itemize}
\item A number of bug fixes and performance improvements to the
  matrix-free framework and related geometric multigrid solvers. In
  particular, the implementation of the Chebyshev iteration, an often
  used smoother in the matrix-free context, has been revised to reduce
  vector accesses. This speeds up matrix-free
  multigrid solvers by up to 10-15\% on geometries with affine
  (parallelogram and parallelpiped) cells, and up to
  5\% on geometries with cells bounded by curved edges and faces.
\marginpar{Luca: Please expand}
\item ParsedConvergenceTable.  
\item The \texttt{FE\_BernardiRaugel} class implements the
  non-standard Bernardi-Raugel (BR) element that can be used as one part of
  a stable velocity/pressure pair for the Stokes equation
  \cite{BR85}. The BR element can be seen as either an enriched
  version of the $Q_1^d$ element with added bubble functions on each
  edge (in 2d) or face (in 3d), or as a reduced version of the $Q_2^d$
  element. It addresses the fact that the $Q_1^d\times Q_0$
  combination is not inf-sup stable (requiring a larger velocity
  space), and that the $Q_2^d\times Q_1$ combination is stable but
  sub-optimal since the velocity space is too large relative to the
  pressure space to provide additional accuracy commensurate with the
  cost of the large number of velocity unknowns. The BR space is
  intermediate to the $Q_1^d$ and $Q_2^d$ spaces.

\item The \texttt{FE\_NedelecSZ} class is an alternative
  implementation of the ideas behind the N{\'e}d{\'e}elec element. It is based
  on the work of Zaglmayr \cite{Zag06} and overcomes the
  sign conflict issues present in traditional N{\'e}d{\'e}lec
  elements that arise from the edge and face parameterizations used
  in the basis functions. Therefore, this element should provide
  consistent results for general quadrilateral and hexahedral
  elements for which the relative orientations of edges and faces as
  seen from all adjacent cells are often difficult to establish.
  The way this element addresses the sign conflict problem is to assign
  local edges and faces a globally defined orientation. The
  implementation is described in \cite{Kynch2017}.
\end{itemize}

Beyond these changes, the changelog lists more than 200 other features and bugfixes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Improved support for automatic and symbolic differentiation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Full support for $hp$ adaptivity in parallel computations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{New and improved tutorial and code gallery programs}

talk about the new programs; also mention updating for C++11 style

@@

\marginpar{Update after the release}
The 9.1 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_0_0_and_9_1_0.html}
     {around 15 incompatible changes}; see \cite{changes91}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions, and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item TODO
\end{itemize}

@@

The two previous releases of \dealii can be cited as
\cite{dealII85,dealII90}.
